%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------


% -----------------------------------------------------------------------------------------------------
% https://www.themuse.com/advice/185-powerful-verbs-that-will-make-your-resume-awesome
% -----------------------------------------------------------------------------------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tfrupee}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{}\vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Abhiroop Mukherjee}} & Email: \href{mailto:abhiroop.m25902@gmail.com}{abhiroop.m25902@gmail.com}\\
  \href{https://www.linkedin.com/in/abhiroop25902/}{LinkedIn: linkedin.com/in/abhiroop25902/} & Mobile: +91{-}8451909828 \\
  \href{https://github.com/Abhiroop25902}{Github:~~~~github.com/Abhiroop25902} \\
\end{tabular*}

%-----------EDUCATION-----------------
\vspace{5pt}
\section{Education}
\resumeSubHeadingListStart{}
\resumeSubheading{Indian Institute of Engineering Science and Technology, Shibpur}{Howrah, India}
{Bachelor of Technology {-} Computer Science and Technology;  CGPA:~9.64}{July 2019 {-} June 2023}
{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Data Structures and Algorithms, Database Management Systems, Operating Systems, Computer Networks}}}

\resumeSubheading{Kendriya Vidyalaya Koliwada}{Mumbai, India}
{10 CGPA AISSE, 2017; 96.2\% AISSCE, 2019}{March 2007 {-} June 2019}
\resumeSubHeadingListEnd{}
\vspace{-5pt}

%-----------Skills-----------------
\vspace{5pt}
\section{Skills Summary}
\resumeSubHeadingListStart{}
\resumeSubItem{Languages:}{~~~~~~~~~~~~~~~~~~~~~JavaScript, TypeScript, Java, Python, C++, HTML, CSS}
\resumeSubItem{Frameworks/Libraries:}{~~~~React, Express, SuiteScript, UIF, TensorFlow, OpenCV, Scikit-learn}
\resumeSubItem{Platforms:}{~~~~~~~~~~~~~~~~~~~~~~NetSuite, Google Cloud, Google Colab}
\resumeSubHeadingListEnd{}

\vspace{-5pt}

%-----------Experience-----------------
\vspace{5pt}
\section{Experience}
\resumeSubHeadingListStart{}

\resumeSubheading{Software Developer}{July 2023 {-} Present}
{\href{https://www.oracle.com/in/index.html}{Oracle India Private Limited}}{Hyderabad}
\resumeItemListStart{}
\resumeItem{}{Built and optimized ERP features across 6 SuiteApps deployed across 3,500+ companies using SuiteScript 2.x, UIF, and SuiteQL.}
\resumeItem{}{Improved financial reporting performance of NFP SuiteApps by 20\% and reduced large transaction dataset page load time from over a minute to 2 seconds (98\% improvement).}
\resumeItem{}{Achieved Top 30 worldwide / Top 3 India in Oracle NetSuite's global AI hackathon with an LLM-based analytics chatbot.}
\resumeItemListEnd{}

\resumeSubheading{Flutter Developer}{Jun 2022 {-} Jul 2022}
{\href{https://evehealthcarecenter.com/}{EVE Healthcare}}{Remote}
\resumeItemListStart{}
\resumeItem{}{Developed the company's mobile application using Flutter, contributing to \rupee37,000 revenue on its launch day.}
\resumeItem{}{Collaborated with two colleagues to deliver a production-ready app that met all functional and business requirements.}
\resumeItemListEnd{}

\resumeSubheading{Project Intern}{June 2022 {-} July 2022}
{\href{https://www.oracle.com/in/index.html}{Oracle India Private Limited}}{Remote}
\resumeItemListStart{}
\resumeItem{}{Developed ERP features for the Transaction Line Distribution SuiteApp, currently deployed across approx. 500 customer accounts serving 600,000+ users.}
\resumeItem{}{Earned a Pre-Placement Offer (PPO) for strong performance.}
\resumeItemListEnd{}


\resumeSubheading{Full Stack Web \& Mobile App Software Intern}{Apr 2021 {-} May 2021}
{\href{https://www.systemonsilicon.com/}{SystemOnSilicon}}{Remote}
\resumeItemListStart{}
\resumeItem{}{Designed the ITX Global website and the SystemOnSilicon website using Bootstrap, HTML and CSS}
\resumeItemListEnd{}
\resumeSubHeadingListEnd{}
\vspace{-5pt}
%-----------PUBLICATION-----------------
\vspace{5pt}
\section{Publications}
\resumeSubHeadingListStart{}
\resumeSubheading{\href{https://link.springer.com/chapter/10.1007/978-981-99-3734-9_25}{Detection of Cipher Types Using Machine Learning Techniques}}{IIEST Shibpur}
{Major Project (CS4291) under the supervision of \href{https://www.iiests.ac.in/IIEST/Faculty/cs-malay}{Prof. Malay Kule}}{Aug 2023}
\resumeItemListStart{}
\resumeItem{}{Achieved 96.72\% classification accuracy across Caesar, Affine, Vigenère, Substitution, and Rail-Fence ciphers using multi-shot prompting on the OPT Transformer model.}
\resumeItemListEnd{}
\resumeSubHeadingListEnd{}
\vspace{-5pt}
%-----------PROJECTS-----------------
\vspace{5pt}
\section{Projects}
\resumeSubHeadingListStart{}

\projectSubheading{\href{https://github.com/Abhiroop25902/bnb-marathon-frontend}{PCOD Nourish - AI Nutrition \& Meal Logging Platform}}{Nov 2025}
\resumeItemListStart{}
\resumeItem{}{Built an AI-driven PCOD nutrition platform using React, Firebase Auth, Firebase Cloud Storage, FireStore DB, and Genkit (Gemini 2.5 Flash).}
\resumeItem{}{Implemented onboarding flows, photo-based meal logging, and an AI recommendation dashboard with scheduled backend automation.}
\resumeItem{}{Won 3rd place at Google Build and Blog Hyderabad hackathon for this end-to-end solution.}
\resumeItemListEnd{}

\projectSubheading{\href{https://github.com/Abhiroop25902/Video-AI-Upscaling}{AI Video Upscaling}}{Feb 2025}
\resumeItemListStart{}
\resumeItem{}{Scaled EDSR Image SuperResolution Model to handle video resolution upscale to three times its original dimensions.}
\resumeItem{}{Reached 2.0 sec/frame on 500$\times$280 inputs and 2.53 sec/frame on 640$\times$360 inputs using a Google Colab dedicated GPU.}
\resumeItem{}{Project has accumulated 56 GitHub stars to date.}
\resumeItemListEnd{}

\projectSubheading{\href{https://github.com/Abhiroop25902/CoWin-Checker}{CoWin Checker}}{June 2021}
\resumeItemListStart{}
\resumeItem{}{Built a Python script that periodically checked CoWin servers for available vaccination slots filtered by location and age group.}
\resumeItem{}{Added OS-level notifications for real-time alerts when slots opened.}
\resumeItem{}{Detected an available vaccination slot within two days of continuous operation.}
\resumeItemListEnd{}

\resumeSubheading{\href{https://github.com/Abhiroop25902/CS-2271-Algo-Lab/tree/master/Assignment\%202/Q2}{Analysis of Disjoint Set Operations}}{IIEST Shibpur}
{Algorithm Lab (CS2771) under the supervision of \href{https://www.iiests.ac.in/IIEST/Faculty/cs-abhik}{Prof. Abhik Mukherjee}}{Apr 2021 {-} May 2021}
\resumeItemListStart{}\vspace{-2pt}
\resumeItem{}{Implemented linked-list-based and tree-based Disjoint Set (Union-Find) data structures in C++.}
\resumeItem{}{Evaluated performance on large real-world graph datasets:}
\vspace{-2pt}
\resumeItemListStart{}
\resumeSubItem{}{KONECT Western USA Roadmap Graph}\vspace{2pt}
\resumeSubItem{}{SNAP Facebook Social Circle Graph}\vspace{2pt}
\resumeSubItem{}{SNAP Epinions Social Network Graph}\vspace{2pt}
\resumeSubItem{}{SNAP LiveJournal Social Network Graph}\vspace{2pt}
\resumeItemListEnd{}
\vspace{2pt}
\resumeItem{}{Measured running times on an Intel Core i5{-}8265U, 8 GB RAM, using WSL Ubuntu on Windows 10.}
\resumeItemListEnd{}

\resumeSubheading{\href{https://github.com/Abhiroop25902/CS-2271-Algo-Lab/tree/master/Assignment\%201}{Analysis of Running Time Complexity of Sorting Algorithms}}{IIEST Shibpur}
{Algorithm Lab (CS2771) under the supervision of \href{https://www.iiests.ac.in/IIEST/Faculty/cs-abhik}{Prof. Abhik Mukherjee}}{Feb 2021 {-} Apr 2021}
\resumeItemListStart{}
\vspace{-2pt}
\resumeItem{}{Generated uniformly and normally distributed datasets as inputs for sorting in C++.}
\resumeItem{}{Implemented Merge Sort, Quick Sort, Randomized Quick Sort, Median-of-Medians Quick Sort, and Bucket Sort as a team of three.}
\resumeItem{}{Analyzed swap counts and execution times across varying input sizes for both distributions.}
\resumeItemListEnd{}

\resumeSubheading{\href{https://github.com/soft-coded/MPNewRepo}{Object Recognition for Observing Social Distancing}}{IIEST Shibpur}
{Minor Project (CS2291) under the supervision of \href{https://www.iiests.ac.in/IIEST/Faculty/cs-samit}{Prof. Samit Biswas}}{Sep 2020 {-} Jan 2021}
\resumeItemListStart{}
\vspace{-2pt}
\resumeItem{}{Deployed a pre-trained YOLOv3 model to detect people in video frames with approximately 90\% accuracy.}
\resumeItem{}{Extended the system to compute pairwise distances between detected individuals to monitor social distancing.}
\resumeItem{}{Collaborated with a 5-member team to scale the pipeline, achieving an average of 8 fps on a Google Colab dedicated GPU.}
\resumeItemListEnd{}


\vspace{-5pt}
\resumeSubHeadingListEnd{}

%-----------Positions Of Responsibility-----------------
\vspace{5pt}
\section{Positions Of Responsibility}
\resumeSubHeadingListStart{}

\resumeSubheading{Flutter Facilitator}{Feb 2022 {-} Mar 2022}
{\href{https://www.youtube.com/channel/UCkArLcgek88KQMbIu2kmygQ}{Google Developers Students Club, IIEST Shibpur}}{IIEST, Shibpur}
\resumeItemListStart{}
\resumeItem{}{As a Flutter Facilitator, I conducted five sessions to provide hands-on experience on app development with Flutter.}
\resumeItem{}{During this period, I also managed a discussion forum to inform all participants regarding doubts and career opportunities.}
\resumeItemListEnd{}

\resumeSubheading{Media Lead}{Aug 2021 {-} Jul 2022}
{\href{https://www.youtube.com/channel/UCkArLcgek88KQMbIu2kmygQ}{Google Developers Students Club, IIEST Shibpur}}{IIEST, Shibpur}
\resumeItemListStart{}
\resumeItem{}{As a Media Lead, my primary objectives are to make sure all the sessions are conducted smoothly, with proper recording and uploading of sessions to YouTube.}
\resumeItem{}{We have successfully conducted 40+ sessions smoothly and are available to watch on our YouTube channel.}
\resumeItemListEnd{}

\resumeSubheading{Video Production Manager}{Jan 2021 {-} Jul 2022}
{\href{https://www.youtube.com/channel/UC6tDcfCbYl8RE7KuFwCVD6w}{CodeIIEST}}{IIEST, Shibpur}
\resumeItemListStart{}
\resumeItem{}{Developed an easy-to-follow methodology for Recording, Editing, and Uploading the CodeIIEST Sessions to YouTube}
\resumeItemListEnd{}

\resumeSubheading{Video Editor}{Sept 2020 {-} Jan 2021}
{\href{https://www.youtube.com/channel/UCgZdehjLg__QLe7bbxxXEYw}{Academic Society of Computer Engineers}}{IIEST, Shibpur}
\resumeItemListStart{}
\resumeItem{}{Edited 12 ASCE Session Recordings of ``The Tech Talk'' using Premiere Pro, for YouTube Uploads}
\resumeItemListEnd{}
\resumeSubHeadingListEnd{}


%-----------Awards-----------------
\vspace{5pt}
\section{Awards}
\begin{description}[font=$\bullet$]
  \item {3rd Position, Google Build and Blog Hackathon, Hyderabad {-} Nov 2025}
  \vspace{-5pt}
  \item {1st Position, Brain Dead, ML Hackathon by ASCE-IIEST {-} Mar 2023}
  \vspace{-5pt}
  \item {284th Rank, Amazon ML Challenge {-} Aug 2021}
  \vspace{-5pt}
  \item {3176th Rank, Google Kickstart Round D {-} Jul 2021}
  \vspace{-5pt}
\end{description}
\vspace{-5pt}

%-----------Certifications-----------------
\vspace{5pt}
\section{Certifications}
\begin{description}[font=$\bullet$]
  \item {\href{https://ude.my/UC-c9298d56-a0ea-4c20-aa43-cfb69113dc68}{Java Programming for Complete Beginners} {-} Udemy, Jun 2025}
  \vspace{-5pt}
  \item {\href{https://www.credly.com/badges/71653a71-8c4f-460f-a274-63d57f3f89c5/public_url}{Basics of Quantum Information} {-} IBM, Aug 2024}
  \vspace{-5pt}
  \item {\href{https://media.licdn.com/dms/document/media/v2/D562DAQEiOWM-L1jCBw/profile-treasury-document-pdf-analyzed/profile-treasury-document-pdf-analyzed/0/1724600153661?e=1764806400&v=beta&t=kfDgF3o1Hc5H_CF6pVtfkzoeHQQVM3mbAc0gLxw4Jfc}{Database Foundations: Intro to Databases} {-} LinkedIn, Aug 2024}
  \vspace{-5pt}
  \item {\href{https://media.licdn.com/dms/document/media/v2/D562DAQEpOu_Cfs-nNQ/profile-treasury-document-pdf-analyzed/profile-treasury-document-pdf-analyzed/0/1724948891415?e=1764806400&v=beta&t=HGR_7e58YHsxdSQ2Ett6-f-i1NKooMPnjknzr1UKmH0}{Learning End-to-End Testing with Jest} {-} LinkedIn, Aug 2024}
  \vspace{-5pt}
  \item {\href{https://www.credly.com/badges/6216881b-da85-4481-a46b-fdc2682dbd09/public_url}{Node.js Essentials} {-} O'Reilly, Aug 2024}
  \vspace{-5pt}
  \item {\href{https://www.coursera.org/account/accomplishments/professional-cert/certificate/4YDYEPYSU5HR}{Google Cybersecurity} {-} O'Reilly, Aug 2024}
  \vspace{-5pt}
  \item {\href{https://media.licdn.com/dms/document/media/v2/D562DAQGXRWZjPTYkIQ/profile-treasury-document-pdf-analyzed/profile-treasury-document-pdf-analyzed/0/1712853365516?e=1764806400&v=beta&t=0WthfVbnTaeSyVhD15tuTrNdx5VO9-8saJeWPWr56as}{React: Creating and Hosting a Full Stack Site} {-} LinkedIn, Apr 2024}
  \vspace{-5pt}
  \item {\href{https://media.licdn.com/dms/document/media/v2/D562DAQENjp6YGbr3SA/profile-treasury-document-pdf-analyzed/profile-treasury-document-pdf-analyzed/0/1699948995097?e=1764806400&v=beta&t=fVrd-gRN0oGUaDviYA4uz1XL14OkB9ZCn6Ww6z1jAmA}{Learning Docker} {-} LinkedIn, Aug 2024}
  \vspace{-5pt}
  \item {\href{https://media.licdn.com/dms/document/media/v2/D562DAQEKq5sgsHkO0A/profile-treasury-document-pdf-analyzed/profile-treasury-document-pdf-analyzed/0/1699949063764?e=1764806400&v=beta&t=K-BZ7OLoYCmpIy9mnH3e0izAWIBrEYWloZfOTu-Lacs}{Scrum: The Basics} {-} LinkedIn, Jan 2021}
  \vspace{-5pt}
  \item {\href{https://media.licdn.com/dms/document/media/v2/D562DAQEJZ9Eif9JaTg/profile-treasury-document-pdf-analyzed/profile-treasury-document-pdf-analyzed/0/1699949143420?e=1764806400&v=beta&t=Az07_isdSAvaev1nZGMQmX3oiHe4dYpM9OXOaQhros8}{Accounting Foundations} {-} LinkedIn, Jan 2021}
  \vspace{-5pt}
  \item {\href{https://learn.nvidia.com/certificates?id=CMBvndSaRPy1UgqyC79Wcg}{Getting Started with Deep Learning} {-} NVIDIA, Jan 2021}
  \vspace{-5pt}
  \item {\href{https://www.coursera.org/account/accomplishments/specialization/certificate/AWLFYFZRNC7K}{Google IT Support Specialization} {-} LinkedIn, Aug 2020}
  \vspace{-5pt}
\end{description}
\vspace{-5pt}

\end{document}